Holomorphic field theories and higher algebra

### 2023-08-17 highervertexops.tex
small tweaks in extension discussion

Let $V$ be a dg vector space and let $V^* = \Hom(V, \CC)$ denote its dual complex. 
Consider the dg Poisson algebra $\cP = \Sym(V \oplus V^*)$ whose Poisson bracket extends the skew-symmetrized evaluation pairing on $V \oplus V^*$.
We view $\cP$ as functions on the cotangent bundle~$T^* V$.
Observe that the quadratic functions form a dg Lie subalgebra
\[
\cP_2 = (\Sym^2(V \oplus V^*), \{-,-\})
\]
of $\cP$.

@@

>>>>

Let $V$ be a dg vector space and let $V^* = \Hom(V, \CC)$ denote its dual complex. 
Consider the dg Poisson algebra $\cP = \Sym(V \oplus V^*)$ whose Poisson bracket extends the skew-symmetrized evaluation pairing on $V \oplus V^*$.
We view $\cP$ as functions on the cotangent bundle~$T^* V$.
Observe that the quadratic functions form a dg Lie subalgebra
\[
\cP_2 = (\Sym^2(V \oplus V^*), \{-,-\})
\]
of $\cP$.
Note that for $V$ a finite-dimensional vector space concentrated in degree zero,
there is a natural identification $\cP_2 = \frak{sp}(T^*V)$, which plays an important role in corollary~\ref{cor:trivforsp}.

@@

On the other hand, this phenomenon does not happen in the most traditional situations.

\begin{cor}
\label{cor:trivforsp}
For $V$ a finite-dimensional vector space concentrated in degree zero, the anomaly $\omega$ is trivial as $\frak{sp}(T^* V) = \cP_2$ is simple and hence $H^2(\cP_2) = 0$.
\end{cor}

In other words, quadratic Hamiltonians (elements of $\cP_2$) admit a natural quantization (lift to $\cW_2$).
Normal ordering offers a method, but there are other choices.

\owen{I am not sure what the status is for infinite-dimensional vector spaces. It seems like functional analysis plays a nontrivial role.}
